---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/poissonconsulting/subreport.svg?branch=master)](https://travis-ci.org/poissonconsulting/subreport)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/subreport?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/subreport)
[![Coverage status](https://codecov.io/gh/poissonconsulting/subreport/branch/master/graph/badge.svg)](https://codecov.io/github/poissonconsulting/subreport?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)

# subreport

`subreport` is an R package to generate `.html` results reports and custom markdown for tables, figures (plots, windows and png files) and (code) blocks saved using the [subfoldr2](https://github.com/poissonconsulting/subreport) package.

The `sbr_knit_results()` function allows the user to view a .html report with all the tables, figures and blocks while the `sbr_tables()`, `sbr_figures()` and `sbr_blocks()` functions produce markdown code complete with headings, numbered labels and captions of their respective objects.

The `sbr_n()` and `sbr_s()` functions allow numbers and strings to be inserted into .Rmd reports.

## Usage

```{r}
library(subfoldr2)
library(subreport)

sbf_set_main(tempdir(), "output")
sbr_set_report(tempdir(), "report")

y <- data.frame(t = 2, comment = "blah blah")
sbf_save_table(y, sub = "Factoids", caption = "A really interesting summary")

cat(sbr_tables())
```

## Installation

To install the latest development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
``` r
install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("subreport")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/subreport/issues).

[Pull requests](https://github.com/poissonconsulting/subreport/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
