---
title: "Title"
author: "LastName, A.A."
bibliography: bibliography.bib
---
  
```{r, echo = FALSE, warning = FALSE, message = FALSE, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE, comment = NA, results = "asis", cache = FALSE)

## README need to set main folder
# subfoldr2::sbf_set_main("../output")
subfoldr2::sbf_reset_sub()

nheaders <- 2L

rename <- c(
  "map" = "Study Area"
)

sort <- c(
  "coef", "map"
)

drop <- NULL
```

## Background

The primary goal of the current analyses is to answer the following questions:
  
  > Is y affected by x?
  
### Data Preparation
  
The data were extracted, cleaned (i.e., checked for errors and corrected if possible), and tidied (i.e., manipulated into a consistent format) using `r substr(R.version.string,1,15)` [@r_core_team_r_2025].

## Results

### Strings

```{r}
cat(subreport::sbr_strings(sort = sort, rename = rename, nheaders = nheaders, drop = drop, tag = ".+"))
```

### Blocks

```{r}
cat(subreport::sbr_blocks(sort = sort, rename = rename, nheaders = nheaders, drop = drop))
```

### Tables

```{r}
cat(subreport::sbr_tables(sort = sort, rename = rename, nheaders = nheaders, drop = drop))
```

### Figures

```{r}
cat(subreport::sbr_figures(sort = sort, rename = rename, nheaders = nheaders, drop = drop))
```

### Numbers

```{r}
cat(subreport::sbr_numbers(sort = sort, rename = rename, nheaders = nheaders, drop = drop))
```

## Acknowledgements

The organizations and individuals whose contributions have made this analytic appendix possible include:
  
- An Organization
  - Someone Else

\newpage

## References